High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 conclusion.tex
wordsmithing to prevent single worded sentences.

We characterized the experience by evaluating the efficiency, scalability and
reliability of both PanDA Broker and AthenaMP as deployed on Titan
(\S\ref{sec:panda_titan}). Our characterization highlighted the strengths and
limitations of the current design and implementation: PanDA Brokers enable
the sustained execution of millions of simulations per week but further work
is required to optimize its efficiency and reliability
(\S\ref{ssec:broker_titan}). PanDA Brokers support the concurrent execution
of multiple AthenaMP instances, enabling each AthenaMP to perform the
concurrent execution of up to 16 Geant4 simulators. Nonetheless, our
characterization showed how improving I/O performance could reduce overheads
(\S\ref{ssec:athenamp_titan}), increasing the overall utilization of Titan's
backfill availability. We introduced PanDA's next generation executor for HPC
systems, characterized its ability to support multi-generation workloads and
analyzed its scaling behavior.  Performance tests on the next generation
executor demonstrate linear strong and weak scalability over several orders
of magnitude  of task and node counts.  Qualitatively, it enables the high-
performance execution of new workloads and advanced execution modes of
traditional workloads.

>>>>

We characterized the efficiency, scalability and reliability of both PanDA
Broker and AthenaMP as deployed on Titan (\S\ref{sec:panda_titan}). Our
characterization highlighted the strengths and limitations of the current
design and implementation: PanDA Brokers enable the sustained execution of
millions of simulations per week but further work is required to optimize its
efficiency and reliability (\S\ref{ssec:broker_titan}). PanDA Brokers support
the concurrent execution of multiple AthenaMP instances, enabling each
AthenaMP to perform the concurrent execution of up to 16 Geant4 simulators.
Nonetheless, our characterization showed how improving I/O performance could
reduce overheads (\S\ref{ssec:athenamp_titan}), increasing the overall
utilization of Titan's backfill availability. We introduced PanDA's next
generation executor for HPC systems, characterized its ability to support
multi-generation workloads and analyzed its scaling behavior.  Performance
tests on the next generation executor demonstrate linear strong and weak
scalability over several orders of magnitude  of task and node counts.
Qualitatively, it enables the high-performance execution of new workloads and
advanced execution modes of traditional workloads.

### 2017-09-10 overall.tex
wordsmithing to prevent single worded sentences.

The metadata I/O breakdown shows that ATLAS jobs yield 23 file \(open()\)
operations per second (not including file \(stat()\) operations) and 5 file
\(close()\) operations per second, with similar distributions. On average,
the maximum number of file \(open()\) operations per job is \(\approx\)170/s
and the maximum number of file \(close()\) operations is \(\approx\)39/s. For
the 1,175 ATLAS jobs observed, the total number of file \(open()\) operations
is 172,089,760 and the total number of file \(close()\) operations is
40,132,992. The difference between these two values is still under
investigation: One possible explanation is that ATLAS jobs don't call a file
\(close()\) operation per every file \(open()\) issued.

>>>>

The metadata I/O breakdown shows that ATLAS jobs yield 23 file \(open()\)
operations per second (not including file \(stat()\) operations) and 5 file
\(close()\) operations per second, with similar distributions. On average,
the maximum number of file \(open()\) operations per job is \(\approx\)170/s
and the maximum number of file \(close()\) operations is \(\approx\)39/s. For
the 1,175 ATLAS jobs observed, the total number of file \(open()\) operations
is 172,089,760 and the total number of file \(close()\) operations is
40,132,992. The difference between these two values is under
investigation: a possible explanation is that ATLAS jobs don't call a file
\(close()\) operation for every file \(open()\) issued.
